---
output:
  pdf_document: default
  html_document: default
---
KAIRUI WU
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Install and Load Packages
library(ggplot2)
library(dplyr)
library(knitr)
library(scales)
library(lubridate)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
loan <- read.csv("prosperLoanData.csv", header = 1, na.strings = c("","NA"))
```

# Introduction of the dataset

Prosper is an American peer-to-peer lending platform. The site allows borrowers 
to post a listing for a chosen loan amount and purpose. Investors are then given 
the opportunity to invest in loans of their choice. Prosper collects data on 
borrower details and provides risk ratings for investors.

The dataset is from the P2P loan platform prosper.com. There are 113937 
observations which contain the information of loans in 81 variables. 

# Univariate Plots Section

```{r echo=FALSE}
# Summary and Structure of the dataset
str(loan)
summary(loan)
```

## Q1.How is the business development of Prosper?
```{r echo=FALSE}
# Count on Listing Loans with Years
loan$Date_ymd <- as.Date(loan$ListingCreationDate, format = "%Y-%m-%d")

ggplot(aes(x = Date_ymd), data = loan) + 
        geom_histogram(aes(color = I('black'),fill = I('#F79420')),
                       binwidth = 365) +
        xlab('Years') + 
        ylab('Count of Listed Loans') +
        scale_x_date(labels = date_format("%Y"), date_breaks='1 year')
```

Based on the plot, the number of listed loans decreased sharply from 2008 to 
2009. This may due to the depression of global economy, for which people don't 
have extra money to do investments and even not believe in the market. After 
2009, with the increasing of the popularity of P2P and the economy was becoming 
stable, people were believing in the market and willing to lend their money to 
others, for which the number of listed loans kept increasing year by year. The 
business development of Prosper is on good trend and very stable these years.

## Q2.How is the lender yield on Prosper?
```{r echo=FALSE,warning=FALSE}
# Count on Lender Yield
ggplot(aes(x = LenderYield), data = loan) +
        geom_histogram(binwidth = 0.05, 
                       aes(color = I('black'),fill = I('#F79420'))) + 
        xlab("Lender Yield") +
        scale_x_continuous(lim = c(quantile(loan$LenderYield, 0.01),
                                   quantile(loan$LenderYield, 0.99)),
                           breaks = seq(0,0.4,0.025))
```

Based on the plot, loans had a lender yield from 0.125 to 0.175 were most 
popular. With the increasing of the lender yiled after 0.175, the number of 
listed loans decreases.

## Q3.What is the distribution of loan purposes on prosper?
```{r echo=FALSE}
# Count on the Category of Loans
loan$ListingCategoryLabel <- factor(loan$ListingCategory, 
                                   labels=c("Not Available", 
                                            "Debt Consolidation", 
                                            "Home Improvement", "Business", 
                                            "Personal loan", "Student Use", 
                                            "Auto", "Other", "Baby & Adoption", 
                                            "Boat", "Cosmetic Procedures", 
                                            "Engagement Ring", "Green Loans", 
                                            "Household Expenses", 
                                            "Large Purchases", 
                                            "Medical/Dental", "Motorcycle", 
                                            "RV", "Taxes", "Vacation", 
                                            "Wedding Loans"))

ggplot(aes(x = ListingCategoryLabel), 
       data = subset(loan, ListingCategoryLabel != 'Not Available')) + 
        geom_bar(aes(color = I('black'),fill = I('#F79420'))) + 
        xlab("Loan Purpose") +
        theme(axis.text.x = element_text(angle = 90)) 
```

The loan with a purpose of debt consolidation is significantly more than others.
This means Prosper is not the first choice for most people to get a loan. 
Getting loans from Prosper is for paying for other loans for most people.

## Q4.What is the distribution of loan amounts on Prosper?
```{r echo=FALSE}
# Count on Loan Amounts
ggplot(aes(x = LoanOriginalAmount), data = loan) + 
        geom_histogram(binwidth = 2000,
                       aes(color = I('black'), fill = I('#F79420'))) +
        xlab("Original Loan Amount") +
        scale_x_continuous(breaks = seq(1000,36000,2000))

summary(loan$LoanOriginalAmount)
```

Based on the plot, the loan with an amount from 1000 to 5000 is significantly 
more than others. 35000 may be the allowable upper limit of the loan on Prosper.

## Q5. What is the count on loan results of Prosper?
For this question, we created the newStatus variable, of which the purpose was 
to divide loans into two groups: good, bad. We regraded the status of "Completed"
and "Current" as "good loan" but other status as "bad loan".
```{r echo=FALSE}
# Count of Loan Status
loan$newStatus <- as.character(loan$LoanStatus)
unique(loan$newStatus)
loan$newStatus[grepl("Completed", loan$newStatus)] <- "Good"
loan$newStatus[grepl("Defaulted", loan$newStatus)] <- "Bad"
loan$newStatus[grepl("Chargedoff", loan$newStatus)] <- "Bad"
loan$newStatus[grepl("Past Due", loan$newStatus)] <- "Bad"
loan$newStatus[grepl("Current", loan$newStatus)] <- "Good"
loan$newStatus[grepl("Cancelled", loan$newStatus)] <- "Bad"
loan$newStatus[grepl("FinalPaymentInProgress", loan$newStatus)] <- "Good"
unique(loan$newStatus)
loan$newStatus <- as.factor(loan$newStatus)

ggplot(aes(x = newStatus), data = loan) + 
        geom_bar(color = I('black'), fill = I('#F79420')) +
        xlab("Loan Status")
```

The number of good loans is three times more than the number of bad loans. Thus,
the management and operation work of Prosper is excellent and the business is of
low risks. Prosper is under good development.

## Q5. What is the distribution of borrowers' employment status on Prosper?
```{r echo=FALSE}
# Count on Employment Status of Borrowers
ggplot(aes(x = EmploymentStatus), 
       data = subset(loan, !is.na(EmploymentStatus) & EmploymentStatus 
                     != 'Not available')) + 
        geom_bar(color = I('black'), fill = I('#F79420')) + 
        theme(axis.text.x = element_text(angle = 90)) + 
        ylim(0,75000) +
        xlab("Employment Status")
```

The employed borrowers were significantly more than unemployed borrowers. 
The full-time employed borrowers were more than part-time borrowers. This 
indicates that the criterion of getting a loan from Prosper is strict and most
unemployed people cannot get a loan from Prosper.

## Q6. What is the distribution of employment durations of borrowers on Prosper?
```{r echo=FALSE}
# Count on Employment Duration
ggplot(aes(x = EmploymentStatusDuration/12), 
       data = subset(loan, !is.na(EmploymentStatusDuration))) + 
        geom_histogram(aes(color = I('black'), fill = I('#F79420')), 
                       binwidth = 0.5) + 
        xlab("Employment Duration") +
        scale_x_continuous(breaks = seq(0,60,2))
```

The longer the employment duration is, the less the number of loans is. This may 
because people who have an entry-level job do not earn much money so that they 
have to borrow the money to do other things or people who start their own 
business in early stage of their career need some money to start. 

## Q7. What is the distribution on borrowers' income ranges?
```{r echo=FALSE}
# Count on Income Range
loan$IncomeRange <- factor(loan$IncomeRange, levels = c("Not employed", 
"$0", "$1-24,999","$25,000-49,999","$50,000-74,999","$75,000-99,999",
"$100,000+"))

ggplot(aes(x = IncomeRange), 
       data = subset(loan, !is.na(IncomeRange) & 
                             IncomeRange != 'Not displayed' & 
                             IncomeRange != '$0')) + 
        geom_bar(aes(color = I('black'), fill = I('#F79420'))) + 
        xlab("IncomeRange") 
```

Based on the plot, borrowers who had an income range frome 25000 to 75000 were 
more than others. Besides, an annual income above 25000 dollors might be a good 
support to get loans from Prosper. Not being employed and having an annual 
income less than 25000 dollors would improve the difficulty to get loans.

## Q8. What is the distribution of borrowers' debt to income ratio on Prosper?
```{r echo=FALSE, warning=FALSE}
# Count on Debt to Income Ratio
ggplot(aes(x = DebtToIncomeRatio), data = loan) + 
        geom_histogram(binwidth = 0.05, 
                       aes(color = I('black'), fill = I('#F79420'))) +
        xlab("Debt to Income Ratio") +
        scale_x_continuous(lim = c(0,1), breaks = seq(0.025,1,0.05)) +
        theme(axis.text.x = element_text(angle = 90))
```

Based on the plot, the debt to income ratio from 0.175 to 0.225 counts most. 
With this indicator increasing, the count decreases. 

# Bivariate Plots Section
## Q9. Is there a change of the lender yield with years on Prosper?
```{r echo=FALSE}
# Change of the Lender Yield with Time
loan$Date_year <- year(loan$Date_ymd)
Year_groups <- group_by(loan, Date_year)
loan.gby <- summarise(Year_groups,
                      Lender_Yield_Median = median(LenderYield))
loan.gby <- arrange(loan.gby, Date_year)
ggplot(aes(x = Date_year, y = Lender_Yield_Median), 
       data = subset(loan.gby, !is.na(Date_year) & 
                             !is.na(Lender_Yield_Median))) +
        geom_line() + 
        scale_x_continuous(breaks = seq(2005,2014,1))
```

In 2011, the lender yield was at the peak. After that year, it kept decreasing. 
The reason may be that P2P loan became increasingly popular these years, for 
which more and more lenders wanted to borrow their money to others through P2P 
platforms. Since the market became more competitive, lenders decreased their 
yields to ensure that their money could be successfully borrowed. The economy 
depression in 2008 also influenced the lender yield.

## Q10. Is there a change of the loan amount with years on Prosper?
```{r echo=FALSE}
# Change of the Loan Amount with Time
loan$Date_year <- year(loan$Date_ymd)
Year_groups <- group_by(loan, Date_year)
loan.gby <- summarise(Year_groups,
                      Loan_Amount_Median = median(LoanOriginalAmount))
loan.gby <- arrange(loan.gby, Date_year)
ggplot(aes(x = Date_year, y = Loan_Amount_Median), 
       data = subset(loan.gby, !is.na(Date_year) & 
                             !is.na(Loan_Amount_Median))) +
        geom_line() + 
        scale_x_continuous(breaks = seq(2005,2014,1))
```

With the increasing popularity of P2P loans and the increasingly strict policy 
and supervision on P2P loans, people were increasingly believing in this kind of 
loans, for which more investors lended money on Prosper. This is the reason why 
the loan amount kept increasing these years.

## Q11. Is there a change of the borrower's credit score with years on Prosper?
```{r echo=FALSE}
# Change of the credit score with Time
ggplot(aes(x = Date_year, y = CreditScoreRangeLower), 
       data = subset(loan, !is.na(Date_year) & !is.na(CreditScoreRangeLower) & 
                             !is.na(EmploymentStatus))) +
        geom_line(stat = "summary", fun.y = mean) + 
        scale_x_continuous(breaks = seq(2003,2014,1))
```

Based on the plot, from 2009, there seemed to be a new criterion for borrowers'
credit scores. With the increasing popularity of P2P loans, more and more people 
who did not have a high credit score started to try to apply loans from prosper,
for which the average credit score of borrowers after 2009 slightly decreased.

## Q12. Is there a change of the number of loans of different results with years?
```{r echo=FALSE, ,warning=FALSE}
# Change of the count of loans of different status with Time
loan$Date_year <- year(loan$Date_ymd)
Year_LoanStatus_groups <- group_by(loan, Date_year, newStatus)
loan.gby_ls <- summarise(Year_LoanStatus_groups,
                      n = n())
loan.gby_ls <- arrange(loan.gby_ls, Date_year, newStatus)

ggplot(aes(x = Date_year, y = n), data = subset(loan.gby_ls, 
                                                !is.na(Date_year) & 
                                                        !is.na(n))) +
        geom_line(aes(color = newStatus)) + 
        scale_x_continuous(lim = c(2006,2013),breaks = seq(2006,2013,1)) +
        ylab("Count_on_Loans")
```

The dataset doesn't contain the whole data of the year 2005 and 2014, so I 
removed these two when doing the research on the count on the loan status. Based 
on the plot, from 2009 to 2013, the count of 'good loan' increased sharply 
whereas the count of 'bad loan' kept almost the same. This means the market 
environment is pretty good these years.

## Q13. What is the differences of the percentage of 'good loans' with various employment status?
```{r echo=FALSE}
# Percentage of Loans of Different Results on Total Counts with Various 
# Employment Status
Employment_LoanStatus_groups <- group_by(loan, EmploymentStatus, newStatus)
loan.gbep_ls <- summarise(Employment_LoanStatus_groups,
                      n = n())
Employment_groups <- group_by(loan, EmploymentStatus)
loan.gbep <- summarise(Employment_groups,
                      totall_count = n())

loan.gbep_ls <- left_join(loan.gbep_ls, loan.gbep,by="EmploymentStatus") 
loan.gbep_ls <- arrange(loan.gbep_ls, EmploymentStatus, newStatus)

ggplot(aes(x = EmploymentStatus, y = n/totall_count), 
       data = subset(loan.gbep_ls, !is.na(EmploymentStatus) & 
                             !is.na(n) & !is.na(totall_count) &
                        EmploymentStatus != 'Not available')) +
        geom_point(aes(color = newStatus)) + ylab("Percentage of Count")
```

From the plot, the percentage of good loans for employed borrowers is higher 
than unemployed. But, it is surprising that the percentage of good loans for 
full-time borrower is lower than that for part-time borrower. Also, 
self-employed borrowers performed better than full-time and part-time borrowers. 
Besides, the retired borrowers performed worst.

## Q14. What is the differences of the percentage of 'good loans' with various income range
```{r echo=FALSE}
# Percentage of Loans of Different Results on Total Counts with Various 
# income range
Income_LoanStatus_groups <- group_by(loan, IncomeRange, newStatus)
loan.gbir_ls <- summarise(Income_LoanStatus_groups,
                      n = n())
Income_groups <- group_by(loan, IncomeRange)
loan.gbir <- summarise(Income_groups,
                      totall_count = n())

loan.gbir_ls <- left_join(loan.gbir_ls, loan.gbir,by="IncomeRange") 
loan.gbir_ls <- arrange(loan.gbir_ls, IncomeRange, newStatus)

ggplot(aes(x = IncomeRange, y = n/totall_count), 
       data = subset(loan.gbir_ls, !is.na(IncomeRange) & 
                             !is.na(n) & !is.na(totall_count) &
                        IncomeRange != 'Not employed')) +
        geom_point(aes(color = newStatus)) + ylab("Percentage of Count")
```

Based on the plot, it is apparently that with the increasing on income ranges, 
the percentage of good loans in total loans increases. The higher the borrower's
income is, the lower the risk of the loan.

## Q15. What is the difference on the employment duration for loans with different results
```{r echo=FALSE, ,warning=FALSE}
# Boxplot of Employment Duration
Loan_Status_groups <- group_by(loan, newStatus)
loan.gbls <- summarise(Loan_Status_groups,
                      n = n())

ggplot(aes(x = newStatus, y = EmploymentStatusDuration), 
       data = subset(loan, !is.na(newStatus) & 
                             !is.na(EmploymentStatusDuration))) +
        geom_boxplot(aes(fill = newStatus)) + 
        scale_y_continuous(lim = c(0,200)) + xlab("Loan Status")
```

The employment status duration of borrowers for good loans is slightly higher
than which is for bad loans. 

## Q16. What is the difference on the debt to income ratio for loans with different results
```{r echo=FALSE, ,warning=FALSE}
# Boxplot of Debt to Income Ratio
Loan_Status_groups <- group_by(loan, newStatus)
loan.gbls <- summarise(Loan_Status_groups,
                      n = n())

ggplot(aes(x = newStatus, y = DebtToIncomeRatio), 
       data = subset(loan, !is.na(newStatus) & 
                             !is.na(DebtToIncomeRatio))) +
        geom_boxplot(aes(fill = newStatus)) + 
        xlab("Loan Status") +
        scale_y_continuous(lim= c(0,0.5))
```

Based on that plot, the debt to income ratio does not have influences on the 
loan status. The mean value and quantile values are almost the same between two 
loan status. This may be because the process of reviewing and the approval on 
the loan focuses much on the debt to income ratio of the applicant of the loan, 
for which the strict process prevent from admitting loans to people who have a 
high debt to income ratio.

## Q17. What is the relationship between loan amount and debt to income ratio?
```{r echo=FALSE, ,warning=FALSE}
# Scatter Plot on Loan Amount and Debt to Income Ratio
ggplot(aes(x = DebtToIncomeRatio, y = LoanOriginalAmount), 
       data = subset(loan, !is.na(DebtToIncomeRatio) & 
                             !is.na(LoanOriginalAmount))) +
        geom_jitter(alpha = 1/20, color = I('orange')) + 
        scale_x_continuous(lim = c(0,1))
```

Based on the plot, large amount loans are only given to borrowers who have a 
debt to income ratio lower than 0.5. The higher the debt to income ratio is, the 
more difficult the person can get such a loan. The loan amount also has an 
apparent level, such as 5000, 10000, 15000, ..., these amounts are popular in 
loans on prosper.

## Q18. What is the difference on BorrowersAPR with different Employment Status? 
```{r echo=FALSE}
# Boxplot of Borrowers APR with Different Employment Status
ggplot(aes(x = EmploymentStatus, y = BorrowerAPR), 
       data = subset(loan, !is.na(EmploymentStatus) & !is.na(BorrowerAPR) & 
                             EmploymentStatus != 'Not available')) + 
  geom_boxplot(aes(fill = EmploymentStatus)) + 
  xlab("Employment Status") +
  ylab("BorrowerAPR") +
  stat_summary(fun.y = mean,geom = 'point',shape = 4) +
  stat_summary(fun.y = mean,geom = 'smooth',aes(group = 1))
```

Based on the plot, full-time employed borrowers and part-time employed borrowers
have the lowest borrower APR. On contrary, unemployed borrowers have the highest
borrower APR. The reason may be that some loans are limited to employed 
borrowers but for unemployed borrowers, there are limited number of loans which 
have high rates that they can apply.

## Q19. What is the difference on Lender Yield with different Prosper Ratings? 
```{r echo=FALSE}
# Boxplot of Lender Yields on Prosper Ratings
loan$ProsperRating..Alpha.<-
  ordered(loan$ProsperRating..Alpha.,levels = c("HR","E","D","C","B","A","AA")) 
ggplot(aes(x = ProsperRating..Alpha., y = LenderYield), 
       data = subset(loan, !is.na(ProsperRating..Alpha.) & 
                             !is.na(LenderYield))) + 
        geom_boxplot(aes(fill = ProsperRating..Alpha.)) +
        xlab("Prosper Rating") + 
        ylab("Lender Yield") +
        stat_summary(fun.y = mean,geom = 'point',shape = 4) +
        stat_summary(fun.y = mean,geom = 'smooth',aes(group = 1))

```

Based on the plot, with the increasing of borrowers' prosper rating, the lender
yield decreases.

# Multivariate Plots Section
## Q20. What is the relationships among BorrowerAPR, LoanAmount and Prosper Rating? 
```{r echo=FALSE}
# Scatter Plot of Borrowers APR with Loan Amount and Prosper Rating
ggplot(aes(x = LoanOriginalAmount, y = BorrowerAPR), 
       data = subset(loan, !is.na(LoanOriginalAmount) & !is.na(BorrowerAPR) & 
                                 !is.na(ProsperRating..Alpha.))) +
                geom_point(aes(color = ProsperRating..Alpha.)) +
                scale_color_brewer(type = 'seq', 
                                   guide = guide_legend(title = 'Prosper Rating',
                                                        reverse = TRUE,
                                                        override.aes = list(
                                                                alpha = 1, 
                                                                size = 2)))
```

Based on the plot, with the increasing of loan amounts, the borrower APR 
decreases. Besides, the higher the prosper rating is, the lower the APR is. 

## Q21. What is the relationship between debt to income ratio with prosper score in different groups of loan? 
```{r echo=FALSE}
# Plot Line on Debt to Income Ratio with Different Prosper Score
ggplot(aes(x = ProsperScore, y = DebtToIncomeRatio), 
       data = subset(loan, !is.na(DebtToIncomeRatio) & !is.na(ProsperScore) & 
                             !is.na(newStatus))) +
        geom_line(stat = 'summary', fun.y = mean, alpha = 1, 
                  aes(color = newStatus))

```

Based on the plot, when the prosper score is low, the debt to income ratio is a
significant indicator to determine the risk of a loan. However, when the prosper
score is high, the debt to income ratio is not so important on the risk of a 
loan.

## Q22. What is the relationship between borrowers APR and debt to income ratio in different groups of employment status? 
```{r echo=FALSE, ,warning=FALSE}
# Scatter Plot of Borrower APR on Debt to Income Ratio
ggplot(aes(x = DebtToIncomeRatio, y = BorrowerAPR), 
       data = subset(loan, !is.na(BorrowerAPR) & !is.na(DebtToIncomeRatio) & 
                             !is.na(EmploymentStatus) & 
                             EmploymentStatus != 'Not available')) +
        geom_point(stat = "summary", fun.y = median, 
                   aes(color = EmploymentStatus)) + 
        scale_x_continuous(lim = c(0,1)) + 
        facet_wrap(~ EmploymentStatus) + geom_smooth(method = 'lm')
```

Based on the plot, the borrower APR has a positive linear relation with the debt
to income ratio for employed borrowers, especially for full-time employed 
borrowers. For unemployed borrowers, the relation is not apparent.

## Q23. What is the relationship between borrowers APR and employment duration in different groups of loan? 
```{r echo=FALSE}
# Scatter Plot of Borrowers APR on Employment Duration
ggplot(aes(x = EmploymentStatusDuration, y = BorrowerAPR), 
       data = subset(loan, !is.na(BorrowerAPR) & 
                             !is.na(EmploymentStatusDuration) & 
                             !is.na(newStatus))) +
        geom_point(stat = "summary", fun.y = median, aes(color = newStatus)) 

```

Based on the plot, when the employment duration is short, the borrower APR is 
significant on the loan risk. People have a short employment duration are not
stable and have less revenues. Therefore, when facing a high APR, these type of
borrowers probably lose the ability to pay the loan due to unemployments and low
revenues. However, for people who have a long employment duration, their 
salaries are always higher and they are more stable, for which APR becomes less 
important to the risk of the loan. 

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x = EmploymentStatus, y = BorrowerAPR), 
       data = subset(loan, !is.na(EmploymentStatus) & !is.na(BorrowerAPR) & 
                             EmploymentStatus != 'Not available')) + 
  geom_boxplot(aes(fill = EmploymentStatus)) + 
  xlab("Employment Status") +
  ylab("BorrowerAPR") +
  stat_summary(fun.y = mean,geom = 'point',shape = 4) +
  stat_summary(fun.y = mean,geom = 'smooth',aes(group = 1)) +
  labs(title="Borrowers APR on Employment Status Groups") +
        theme(plot.title = element_text(hjust = 0.5))
```

### Description One
Based on the plot, full-time employed borrowers and part-time employed borrowers
have the lowest borrower APR. On contrary, unemployed borrowers have the highest
borrower APR. The reason may be that some loans are limited to employed 
borrowers but for unemployed borrowers, there are limited number of loans which 
have high rates that they can apply.

### Plot Two
```{r echo=FALSE, Plot_Two}
Employment_LoanStatus_groups <- group_by(loan, EmploymentStatus, newStatus)
loan.gbep_ls <- summarise(Employment_LoanStatus_groups,
                      n = n())
Employment_groups <- group_by(loan, EmploymentStatus)
loan.gbep <- summarise(Employment_groups,
                      totall_count = n())

loan.gbep_ls <- left_join(loan.gbep_ls, loan.gbep,by="EmploymentStatus") 
loan.gbep_ls <- arrange(loan.gbep_ls, EmploymentStatus, newStatus)

ggplot(aes(x = EmploymentStatus, y = n/totall_count), 
       data = subset(loan.gbep_ls, !is.na(EmploymentStatus) & 
                             !is.na(n) & !is.na(totall_count) &
                        EmploymentStatus != 'Not available')) +
        geom_point(aes(color = newStatus)) + ylab("Percentage of Count") +
        scale_color_discrete(name="Loan Status") + 
        scale_y_continuous(labels = percent, breaks = seq(0,1,0.05)) +
        labs(title="Percentage of Loans with Different Status on Employment 
             Status Group") +
        theme(plot.title = element_text(hjust = 0.4))
```

### Description Two
From the plot, the percentage of good loans for employed borrowers is higher 
than unemployed. But, it is surprising that the percentage of good loans for 
full-time borrower is lower than that for part-time borrower. Also, 
self-employed borrowers performed better than full-time and part-time borrowers. 
Besides, the retired borrowers performed worst.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = EmploymentStatusDuration, y = BorrowerAPR), 
       data = subset(loan, !is.na(BorrowerAPR) & 
                             !is.na(EmploymentStatusDuration) & 
                             !is.na(newStatus))) +
        geom_point(stat = "summary", fun.y = median, aes(color = newStatus),
                   alpha = 1/2) +
        scale_color_discrete(name="Loan Status") +
        scale_x_continuous(breaks = seq(0,800,50)) +
        scale_y_continuous(breaks = seq(0,0.5,0.05)) +
        xlab("Employment Status Duration (Unit:Days)") +
        ylab("Borrowers APR") +
        labs(title = "The Ralationship Between Borrowers APR and Employment 
             Duration") +
        theme(plot.title = element_text(hjust = 0.4))
```

### Description Three 
Based on the plot, when the employment duration is short, the borrower APR is 
significant on the loan risk. People have a short employment duration are not
stable and have less revenues. Therefore, when facing a high APR, these type of
borrowers probably lose the ability to pay the loan due to unemployments and low
revenues. However, for people who have a long employment duration, their 
salaries are always higher and they are more stable, for which APR becomes less 
important to the risk of the loan. 

------

# Reflection
In the analysis, the first difficulty I met was the lack of integraty of data
with time series. I solved it by limiting the time period. The second one was 
the complexity of variables. Some categorical variables have 8 - 10 labels. To 
solve this point, I created several new variables to re-categorize the values to
make the analysis easy. The third one was I was lack of the knowledge of finance,
for which it was not easy to understand some variables in this dataset. I just 
tried my best to get a good understanding on variables and ignored the variables
which were not easy to understand.

For future work, there are some point that can be further explored. Firstly, the 
loan status was transfferd to a simple representation in my research. Instead of
just two labels (good, bad) in this variable, we can use the original loan 
status variable which is more complex to do in-depth research. Besides, more 
features can be considerred in the research in future, for which we may find
more patterns and more relationships between variables. In addition, predictive
data analytics method can be applied on the research.

